---
title: "hw5_sc4456"
author: "Siyan Chen"
date: "11/3/2018"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)

```

# Problem 1

read all data

```{r, message=FALSE}
file_list = list.files(path = "./data") 
df = str_c("./data/", file_list) 
# create correct subpath format
new_file_list= str_remove(file_list, "\\.csv$")
# remove .csv 
data_read = data.frame(new_file_list) %>% 
mutate(file_read = map(.x = df, ~read_csv(.x))) %>% 
  unnest()
head(data_read)
```

tidy data  

```{r}
tidy_data = data_read %>%
  janitor::clean_names() %>% 
  separate(new_file_list, into = c("group", "subject_id"), sep = "_") %>% 
  gather(key = "week", value = value, week_1:week_8) %>% 
  mutate(subject_id = as.numeric(subject_id), week = str_remove(week, "week\\_")) %>% 
  mutate(week = as.numeric(week), value = as.numeric(value))
head(tidy_data)
```

Plot

```{r}
tidy_data$participants = paste(tidy_data$group, tidy_data$subject_id)
# create a variable to make subject_id unique(control1 is not exp 1)
tidy_data %>% 
  ggplot(aes(x = week, y = value, color = participants)) + geom_line() + facet_grid(~group)
```

Comment: Based on the plot, the subjects of experimental group has slightly higher value at the beginning compared to control. The value of Sunbjects in experimenatl arm increase over weeks while the control group has no trend.

# Problem 2

get dat
```{r}
require(RCurl)
homicide_data = read.csv(text = getURL("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"))
# method I find online to get the data
```

This dataset has `r ncol(homicide_data)` variables and `r nrow(homicide_data)` observations. Variables include `victim last` `victim first` name, `victim age`, `victim race` and others.

tidy
```{r}
homicide_data$city_state = paste(homicide_data$city, homicide_data$state) 
# create a new variable 
homicid_data_tidy = homicide_data %>% 
select(-city, -state) %>% 
# and remove the repeated information 
  mutate(disposition = as.character(disposition))
# change to character to detect the string

dfa = homicid_data_tidy %>% 
  group_by(city_state) %>% 
  summarize(total_number = n()) 
# create one dataframe dfa to save city_state and total number of homicide

dfb = homicid_data_tidy %>% 
  mutate(solved = str_detect(homicid_data_tidy$disposition, "Closed by arrest")) %>% 
  group_by(city_state, solved) %>% 
  summarize(number_solved = n()) %>% 
  filter(solved == TRUE)
# get the number of solved homicide for each city

homicide_summarise = merge(dfa, dfb, by = "city_state") %>% 
  mutate(number_unsolved = total_number - number_solved) %>% 
  select(-solved, -number_solved) 
# make a summarize to get the total number of homicide and number of unsolved homicide for each city. 
head(homicide_summarise)
```


```{r}
Baltimore_MD = homicide_summarise %>% 
  filter(city_state == "Baltimore MD") 
prop_test_Baltimore_MD = prop.test(Baltimore_MD$number_unsolved, Baltimore_MD$total_number)
tidy_prop_test_Baltimore_MD = broom::tidy(prop_test_Baltimore_MD)
tidy_prop_test_Baltimore_MD %>% pull(estimate) 
tidy_prop_test_Baltimore_MD %>% pull(5) 
tidy_prop_test_Baltimore_MD %>% pull(6)
# ??? how to pull a confidence interval 
```


```{r}
total_homicide = homicide_summarise %>% 
  select(-3)
unsolved_homicide = homicide_summarise %>% 
  select(-2)
city_prop  = homicide_summarise %>% 
  mutate(parameters = map2(unsolved_homicide$number_unsolved,
                           total_homicide$total_number,
                           prop.test )) %>% 
  mutate(parameters = map(parameters, broom::tidy)) %>% 
  unnest() %>% 
  select(1,2,3,4,8,9) %>% 
  janitor::clean_names()


```


plot

```{r}
city_prop %>% 
  mutate(city_state = fct_reorder(city_state, desc(estimate))) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



